Analysis methods for characterizing the climate sensitivity of annual growth and woody productivity using tree-rings

### 2020-05-21 doc/methods/analysis_methods.Rmd
update analysis methods
#27

1.3. Use the [climwin](https://cran.r-project.org/web/packages/climwin/index.html) R package [(van de Pol et. al. 2016)](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12590), to identify the climate variables and time windows that most strongly influences tree growth *for all species combined*. 
Climwin can check for linear and quadratic relationships. We checked quadratic only because (i) it speeds up the process, (ii) preliminarly tests revealled that quadratic was usually the one with lower AIC, and when not there tended to be little difference in AIC and the curve would look like a straight line anyway, (iii) quadratic makes more biological sense, (iv) it would be too tricky to code the gam to adapt to any circumstance.
We put the residuals derived in step 1.1 in *climwin* with a mixed effects model using species and tree identity as random effect: `residual ~ [climate] + (1 | sp) + (1 | treeID)`. 
Outputs are saved [here](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/results/ALL_species_mixed_model_on_residuals/). Example output is shown in Fig. 1.

@@

2.2. For each species independently, run GAM models including every combination of climate variables (as a 2-degree polynomial to allow quadratic curve), spline of DBH (3 knots), and splines of year fit to each individual as a random effect.
`ln[response variable] ~ spline(DBH) + quad([climate variables]) + spline(year, with treeID as random effect)`

>>>>

1.3. Use the [climwin](https://cran.r-project.org/web/packages/climwin/index.html) R package [(van de Pol et. al. 2016)](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12590), to identify the climate variables and time windows that most strongly influences tree growth *for all species combined*. 
Climwin can check for linear and quadratic relationships. We checked quadratic only because (i) it speeds up the process, (ii) preliminarly tests revealled that quadratic was usually the one with lower AIC, and when not there tended to be little difference in AIC and the curve would look like a straight line anyway, (iii) quadratic makes more biological sense, (iv) it would be too tricky to code the GAM to adapt to any circumstance.
We put the residuals derived in step 1.1 in *climwin* with a mixed effects model using species and tree identity as random effect: `residual ~ [climate] + (1 | sp) + (1 | treeID)`. 
Outputs are saved [here](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/results/ALL_species_mixed_model_on_residuals/). Example output is shown in Fig. 1.

@@

2.2. For each species independently, run GAM models including every combination of climate variables (as a 2-degree polynomial to allow quadratic curve), and fit one year spline for each treeID, plus a random intercept for each tree. We will also run models with a spline of DBH (3 knots).

 `uGamm(log(core_measurement) ~ ns(wet, 2) + ns(tmx, 2)+ s(Year, by = treeID), random = list(treeID = ~1), data = x, na.action = "na.fail")`
